Improved Approximation Algorithms for the Maximum Carpool Matching Problme

### 2016-12-19 src/group.tex
outline
group

In this section we introduce the group carpool and show that it does not fit the
submodular maximization formulation while the local search algorithm handle it
without any modification.

>>>>

In this section we introduce the group carpool and show that it does not fit the
submodular maximization formulation.
We show, however, that the problem still has a 
$\frac{1}{2} - \varepsilon$-approximation algorithm.
Finally, we argue that the local search algorithm can be trivially generalized
to handle the new variant of the problem while keeping the same approximation
guarantees.

We start by giving an example why the maximum \textsc{group carpool} problem can
not be formalized as an unconstrained submodular maximization problem as
before.
Considered the instance given in Figure~\ref{fig:not submodular}

\begin{figure}
\caption{
\label{fig:not submodular}
Consider the following instance where node capacity are written inside nodes, 
arcs are labeled with their size and all weights are equal to 1.
It is easy to see that if $f(S)$ is the optimal solution where $S$ is the set of
drivers, then $f(A) + f(B) = 2 \leq 3 = f(A \cup B) + f(A \cap B)$,
thus, $f$ is not submodular. 
}
\begin{center}
\input{fig-not-submodular}
\end{center}
\end{figure}
